Object Naming in Language and Vision: A Survey and a New Dataset

### 2019-11-28 papers/LREC2020/background.tex

\begin{table*}[htb]
  \centering
  \begin{tabular}{lrrrrr}
    \toprule
    &   RefCoco/+  &  Flickr30kE &           VG &      VGmn &        MN \\
    \midrule
    \# objects & 50.000 & 243.801 & 3.781.232 & 25.223 & 25.315 \\
    naming vocab size &  5.004 &  10.423 &   105.441 &  1.061 &  7.970 \\
    av. annotations/object &      2.8 &       2.3 &         1.7 &      7.2 &     35.3 \\
    \% objects with n types $>$ 1 &      0.7 &       0.3 &         0.02 &      0.1 &      0.9 \\
    av. types/object &      1.9 &       1.4 &         1 &      1.1 &      5.7 \\
    \bottomrule
  \end{tabular}
  \label{tab:compare}
  \caption{Overview statistics for different data sets containing object naming data. VGmn shows statistics for the subset of \vg that overlaps with our ManyNames dataset. \gbt{What is the VGmn column? Is it necessary?} \sz{VGmn refers to the subset of images in VG that appear in MN. This shows that the images we selected for ManyNames also have more annotations in VG. I think this is useful to know.} \gbt{ok! We'll need to explain why the number of objects not identical.}}
\end{table*}

>>>>

\begin{table*}[htb]
  \centering
  \begin{tabular}{lrrrrr}
    \toprule
    &   RefCoco/+  &  Flickr30kE &           VG &      VGmn &        MN \\
    \midrule
    \# objects & 50.000 & 243.801 & 3.781.232 & 25.315 & 25.315 \\
    naming vocab size &  5.004 &  10.423 &   105.441 &  1.061 &  7.970 \\
    av. annotations/object &      2.8 &       2.3 &         1.7 &      7.2 &     35.3 \\
    \% objects with n types $>$ 1 &      0.7 &       0.3 &         0.02 &      0.05 &      0.9 \\
    av. types/object &      1.9 &       1.4 &         1 &      1.1 &      5.7 \\
    \bottomrule
  \end{tabular}
  \label{tab:compare}
  \caption{Overview statistics for different data sets containing object naming data. VGmn shows statistics for the subset of \vg that overlaps with our ManyNames dataset.}
\end{table*}

### 2019-11-28 papers/LREC2020/conclusion.tex
Analysis section polished

The question of how people choose names for objects presented visually is relevant for Computational Linguistics (especially Language \& Vision), Computer Vision, Cognitive Science, and Linguistics.
% The object naming variation attested in the ManyNames dataset offers new challenges and perspectives, both for practical modeling approaches in Language \& Vision as well as for theoretical work in (Psycho-)linguistics.
We have surveyed datasets that can be useful to address this question, and proposed a new dataset, ManyNames, that affords new possibilities, both for analysis and modeling, providing a means
(i) to study how different people would name the same object (image region), and, given a specific name, estimate its degree of preference, which might vary substantially across different instances of a class, and   
(ii) to obtain a set of possible names for individual objects, as well as available lexical alternatives for specific names, which again might vary strongly across instances and often cannot be retrieved from existing taxonomies like WordNet.

\gbt{The following needs to be made more coherent}
For Computer Vision and L\&V, our data highlights the fact that bounding boxes are often ambiguous, which affects model performance on object categorization and naming.
Crucially, evaluations in these task assume that object identification is possible based on the bounding box, and evaluates only the categories or names of objects assuming they are unique.
The naming variation we have found also challenge the common assumption that there exists a single canonical name for individual visual objects (also see \cite{deng2014large,wang2014poodle,peterson2018learning}).
At the same time, the ability to distinguish incorrect object names from good alternatives is essential for visual object understanding.
Our data allows models to be tested wrt their ability to account for naming variants of an instance: For instance, to what extent the top N predicted are names valid alternatives (\textsl{dog, animal, pet} vs. \textsl{dog, hat, grass}). 
\gbt{We have to be careful; without the correction round this is not strictly speaking true. How can we phrase this?}
% Wang et al.: ". The hypothesis is that by modeling the variation in granularity levels for different concepts, we can gain a more informative insight as to how the output of image annotation systems can relate to how a person describes what he or she perceives in an image, and consequently produce image annotation systems that are more human-centric."
% @related work
%[For example, \newcite{peterson2018learning} train CNN classifiers on objects with multiple labels which stand in a hierarchical relation (e.g., dog, animal) in order to learn better visual representations which capture the hierarchical structure of a taxonomy. \cs{remove or move to related work? also sentence to Ordonez}]
%\footnote{Other work used training data with multiple labels per image to improve image classification performance on images with multiple objects (e.g.,~Wang et al., 2016 REF). \cs{maybe remove, since it is not that relevant?}}
% peterson2018learning: discuss the bias introduced into learned representations by training on data of  single label annotations ("labels cut arbitrarily across natural psychological taxonomies, e.g., dogs are separated into breeds but never categorized as dogs").

@@

\gbt{Make the following coherent with the previous paragraph}
Our data indeed indicates a tendency for particular instances marked by bounding boxes to elicit a preferred name across subjects, which is in line with existing theoretical research on object naming and categorization. 
However, we show that there is also consistent variation in naming, and even high variability in agreement across instances within the same class or domain.
The latter suggests that there are specific visual characteristics of either the object itself or the visual context in which it appears that trigger variation. With prototypical pictures (see Figure\ \ref{fig:cake}), as done in traditional studies, this observation would not be possible.
We moreover find that much of the variation in object naming cannot be explained by adopting a traditional taxonomy-driven and hierarchical view, which has been dominant in the literature, both in theoretical and in computational approaches.

>>>>

% To sum up, we find both substantial consistency in naming (the most frequent name accounts for 75\% of object names, on average) and substantial naming variation (the remaining 25\%). Moreover, there is a very large standard variation in how much agreement there is for objects in images, that only partially depend on the domain.

The question of how people choose names for objects presented visually is relevant for Language and Vision, Computational Linguistics, Computer Vision, Cognitive Science, and Linguistics.
We have surveyed datasets that can be useful to address this question, and proposed a new dataset, ManyNames, that affords new possibilities both for analysis and modeling of object naming.
% gbt: commenting the following out cause it's a bit dangerous to say this without the verification phase.
% , providing a means
% (i) to study how different people would name the same object (image region), and, given a specific name, estimate how likely people are to use it for a given object, which might vary substantially across different instances of a given category, and
% (ii) to obtain a set of possible names for individual objects, as well as available lexical alternatives for specific names, which again might vary strongly across instances and often cannot be retrieved from existing taxonomies like WordNet.

For Computer Vision and L\&V, our data highlights the fact that bounding boxes are often ambiguous, which can affect model performance on object categorization and naming.
Crucially, evaluations in these tasks assume that object identification is possible based on the bounding box. 
Our data suggests that this is not always the case and provides empirical data to for instance asses whether model mistakes are plausible (similar to those of humans, as in the \word{toy/book/bed} case) or really off.
% (as in the case where they label objects as the background, like \word{grass} for \word{dog}).

Moreover, standard evaluations assume that object names (or categories) are unique.
% The naming variation we have found also challenge the common assumption that there exists a single canonical name for individual visual objects (also see \cite{deng2014large,wang2014poodle,peterson2018learning}).
The ability to distinguish incorrect object names from good alternatives is essential for visual object understanding.
Our data provides a first step towards enabling model evaluation on naming variants of an instance, checking for instance to what extent the top N predicted are names valid alternatives (\textsl{dog, animal, pet}) or not (\textsl{dog, hat, grass}).
However, to fully enable this sort of analysis, a further annotation step is needed, to account for the referential uncertainty of bounding boxes and annotation noise.
We plan to take this step in future work, which will also enable more robust conclusions with respect to naming variation.

% Wang et al.: ". The hypothesis is that by modeling the variation in granularity levels for different concepts, we can gain a more informative insight as to how the output of image annotation systems can relate to how a person describes what he or she perceives in an image, and consequently produce image annotation systems that are more human-centric."
% @related work
%[For example, \newcite{peterson2018learning} train CNN classifiers on objects with multiple labels which stand in a hierarchical relation (e.g., dog, animal) in order to learn better visual representations which capture the hierarchical structure of a taxonomy. \cs{remove or move to related work? also sentence to Ordonez}]
%\footnote{Other work used training data with multiple labels per image to improve image classification performance on images with multiple objects (e.g.,~Wang et al., 2016 REF). \cs{maybe remove, since it is not that relevant?}}
% peterson2018learning: discuss the bias introduced into learned representations by training on data of  single label annotations ("labels cut arbitrarily across natural psychological taxonomies, e.g., dogs are separated into breeds but never categorized as dogs").

@@

Our current data clearly supports the prediction in theoretical research on object naming and categorization that there will in general be a preferred name for a given visually presented object.
It also tentatively suggests that (a) there is also consistent variation in naming, with an average of almost three elicited names per instance; (b) much of this variation cannot be explained by adopting a traditional taxonomy-driven and hierarchical view, which has been dominant in the literature, both in theoretical and in computational approaches; (c) there is high variability in agreement across instances within the same domain.
The latter suggests that there are specific visual characteristics of either the object itself or the visual context in which it appears that trigger variation. With prototypical, idealized pictures of the sort used in traditional studies (see Figure\ \ref{fig:cake}), this observation would not be possible.

We hope that ManyNames triggers more empirical research on object naming, a topic that has been understudied in both computational and theoretical approaches to language.

### 2019-11-28 papers/LREC2020/data-collection.tex
Figure with MN examples modified
Analysis section polished

\begin{table*}[htp]
	\small
	\centering
	\begin{tabular}{@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l}
		\toprule
		vehicles &            food & animals\_plants &           home &        buildings &             people &      clothing \\
		\midrule
		train (954) &  pizza (518) &  giraffe (915) &  bed (888) &  house (340) &  boy (853) &  shirt (904) \\
		car (642) &  cake (261) &  horse (822) &  bench (714) &  bridge (274) &  man (806) &  jacket (451) \\
		plane (485) &  bread (186) &  cat (754) &  table (687) &  dugout (91) &  woman (766) &  coat (267) \\
		airplane (479) &  sandwich (153) &  dog (654) &  desk (672) &  tent (53) &  girl (650) &  dress (190) \\
		motorcycle (466) &  bun (143) &  zebra (461) &  counter (516) &  restaurant (33) &  lady (342) &  hat (77) \\
		% truck (465) &  cheese (110) &  cow (324) &  couch (366) &  overpass (23) &  guy (330) &  t-shirt (62) \\
		% boat (450) &  donut (78) &  bird (295) &  chair (365) &  grill (22) &  child (230) &  tie (51) \\
		% jet (106) &  salad (70) &  sheep (216) &  carpet (307) &  garage (18) &  batter (110) &  blazer (43) \\
		% aircraft (85) &  sauce (68) &  bull (48) &  bowl (219) &  hotel (16) &  kid (85) &  hood (26) \\
		% van (76) &  apple (33) &  flower (40) &  curtain (182) &  castle (14) &  skateboarder (80) &  cap (20) \\
		\bottomrule
	\end{tabular}
	\caption{Overview of the ManyNames dataset: Top 5 VG names for each domain (number of instances in parentheses). %\textbf{double-check}
		\label{tab:overview_dataset1}}
\end{table*}

\begin{figure*}[htp]
  \centering
  \includegraphics[width=1.5\columnwidth]{figures/round0.png}
  \caption{Instructions for AMT annotators for the first round.}
  \label{fig:instructions1}
\end{figure*}

@@

We then retrieved all VG images depicting an object whose name matches or is subsumed by words in one of these synsets; we refer to these words as \textit{seeds} ($450$\ in total).
%\gbt{from the dataframe it's 449. Also, there are some mistakes ('dugout.', 'man's').+++
We did not consider objects with names in plural form, with parts-of-speech other than nouns\footnote{We obtained tags with CoreNLP \cite{manning2014stanford}.}, or that were multi-word expressions (e.g.,~\textsl{pink bird}). 
We further only considered objects whose bounding box covered~\mbox{$20-90\%$} of the image area.
% We based the definition of our set of nodes on the WN (REF) synsets of the McRae concepts (e.g.,~dog, duck, goose, gull), the nominal WordNet hierarchy, and the frequency distribution of the VG object names' synsets.\footnote{TODO: need to be clear from the general description of VG that the frequ. of instances labeled with the synset of the object name is meant.} 
% First, we selected a set of collection node candidates---synsets which match (e.g.,~\textsl{dog, duck, goose, gull}) or subsume (e.g.,~\textsl{mammal, bird}) the McRae synsets\footnote{Specific synset IDs, e.g.,~dog.n.01, are omitted for readability.}. 
% From these candidates we kept those as collection nodes which had a high frequency of VG object instances of different names. For example, VG instances  subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck, goose}, or \textsl{gull} did not have name variants in VG, so we kept \textsl{dog} and \textsl{bird} as collection nodes.
%\paragraph{Collection of instance candidates}
% Goal of above procedure was the collection of instances of selected object classes---our nodes--- whose VG names correspond to or subsume (are hypernyms of) a McRae concept, and whose object names differ, that is, of which we can expect that people possess different names for them (e.g.,~\textsl{duck, goose, gull} for \textsl{bird}).
% \paragraph{Sampling of instances}
Because of the Zipfian distribution of names, and to balance the collection, we sampled instances depending on the size of the seeds: up to $500$\ instances for seeds with up to $800$\ objects, and up to $1000$\ instances for larger seeds. This yielded a dataset of\ $31,093$~instances, which was further pruned during annotation, as explained next.
Table~\ref{tab:overview_dataset1} shows the top 5 \vgenome names in each of the domains.

>>>>

\begin{table*}[htp]
	\small
	\centering
	\begin{tabular}{@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l@{~}l}
		\toprule
		vehicles &            food & animals\_plants &           home &        buildings &             people &      clothing \\
		\midrule
		train (954) &  pizza (518) &  giraffe (915) &  bed (888) &  house (340) &  boy (853) &  shirt (904) \\
		car (642) &  cake (261) &  horse (822) &  bench (714) &  bridge (274) &  man (806) &  jacket (451) \\
		plane (485) &  bread (186) &  cat (754) &  table (687) &  dugout (91) &  woman (766) &  coat (267) \\
		airplane (479) &  sandwich (153) &  dog (654) &  desk (672) &  tent (53) &  girl (650) &  dress (190) \\
		motorcycle (466) &  bun (143) &  zebra (461) &  counter (516) &  restaurant (33) &  lady (342) &  hat (77) \\
		% truck (465) &  cheese (110) &  cow (324) &  couch (366) &  overpass (23) &  guy (330) &  t-shirt (62) \\
		% boat (450) &  donut (78) &  bird (295) &  chair (365) &  grill (22) &  child (230) &  tie (51) \\
		% jet (106) &  salad (70) &  sheep (216) &  carpet (307) &  garage (18) &  batter (110) &  blazer (43) \\
		% aircraft (85) &  sauce (68) &  bull (48) &  bowl (219) &  hotel (16) &  kid (85) &  hood (26) \\
		% van (76) &  apple (33) &  flower (40) &  curtain (182) &  castle (14) &  skateboarder (80) &  cap (20) \\
		\bottomrule
	\end{tabular}
	\caption{Overview of the ManyNames dataset: Top 5 VG names for each domain (number of instances in parentheses).\label{tab:overview_dataset1}}
\end{table*}

\begin{figure*}[htp]
  \centering
  \includegraphics[width=1.5\columnwidth]{figures/round0_cropped.png}
  \caption{Instructions for AMT annotators for the first round (whole instructions showed more examples, see Figure~\ref{fig:instructions2}).}
  \label{fig:instructions1}
\end{figure*}

@@

We then retrieved all VG images depicting an object whose name matches or is subsumed by words in one of these synsets; we refer to these words as \textit{seeds} ($450$\ in total).
\gbt{from the dataframe in the github it's 449. Also, there are some mistakes in the list of seeds ('dugout.', 'man's') -- to check after the deadline.}
We did not consider objects with names in plural form, with parts-of-speech other than nouns\footnote{We obtained tags with CoreNLP \cite{manning2014stanford}.}, or that were multi-word expressions (e.g.,~\textsl{pink bird}). 
We further only considered objects whose bounding box covered~\mbox{$20-90\%$} of the image area.
% We based the definition of our set of nodes on the WN (REF) synsets of the McRae concepts (e.g.,~dog, duck, goose, gull), the nominal WordNet hierarchy, and the frequency distribution of the VG object names' synsets.\footnote{TODO: need to be clear from the general description of VG that the frequ. of instances labeled with the synset of the object name is meant.} 
% First, we selected a set of collection node candidates---synsets which match (e.g.,~\textsl{dog, duck, goose, gull}) or subsume (e.g.,~\textsl{mammal, bird}) the McRae synsets\footnote{Specific synset IDs, e.g.,~dog.n.01, are omitted for readability.}. 
% From these candidates we kept those as collection nodes which had a high frequency of VG object instances of different names. For example, VG instances  subsumed by McRae's \textsl{dog} were named \textsl{beagle, greyhound, puppy, bulldog}, etc., while McRae's \textsl{duck, goose}, or \textsl{gull} did not have name variants in VG, so we kept \textsl{dog} and \textsl{bird} as collection nodes.
%\paragraph{Collection of instance candidates}
% Goal of above procedure was the collection of instances of selected object classes---our nodes--- whose VG names correspond to or subsume (are hypernyms of) a McRae concept, and whose object names differ, that is, of which we can expect that people possess different names for them (e.g.,~\textsl{duck, goose, gull} for \textsl{bird}).
% \paragraph{Sampling of instances}
Because of the Zipfian distribution of names, and to balance the collection, we sampled instances depending on the size of the seeds: up to $500$\ instances for seeds with up to $800$\ objects, and up to $1000$\ instances for larger seeds. This yielded a dataset of\ $31,093$~instances, which was further pruned during annotation, as explained next.
Table~\ref{tab:overview_dataset1} shows the top 5 \vgenome names in each of the domains.

### 2019-11-28 papers/LREC2020/intro.tex

\sz{what do we say about the availability of the dataset?}
Generally, research in Language \& Vision (L\&V) is interested in modeling how speakers \textit{naturally} talk about visual objects and scenes, in contrast to fixed image labeling schemes used in Computer Vision. 
Data collections in L\&V are typically set up as free annotation tasks,  where annotators (or speakers) are free to produce whatever word or utterance they consider most suitable for the given task (e.g.\ image description, reference to objects, visual dialogue) -- which necessarily results in linguistic variation.
For this reason, large-scale data collections in L\&V usually provide a certain amount of parallel annotations for the same entity from different annotators \cite{fangetal:2015,devlin:imcaqui,Kazemzadeh2014,mao15,vries2017guesswhat}.

As compared to work on perception and language grounding in linguistics or cognitive science, however, recent data collections in L\&V capture a rather limited amount of inter-speaker variation.
For instance, so-called picture naming norms used in psycholinguistics typically record ``annotations'' for hundreds of speakers for the same object  \cite{snodgrass,rossion2004revisiting}, whereas captioning or referring expression data sets typically provide less than 10 annotations per entity \cite{devlin:imcaqui,Kazemzadeh2014,mao15}.
Consequently, a reliable assessment of inter-annotator agreement, speaker preferences and a deeper linguistic analysis of the observed variation is mostly out of scope with available data collections in  L\&V.
At the same time, these data sets provide more realistic images of real-world objects and scenes, and a wider coverage of object categories whereas picture naming norms have been collected for idealized graphical objects, as shown in Figure \ref{fig:cake}.

In this paper, we take a first step at studying natural naming of objects in real-world images. We believe that a more systematic understanding of the factors underlying variation in object naming could inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, but also the design of models and architectures in L\&V that deal with a large and natural vocabulary \cite{lazaridou-dinu-baroni:2015:ACL-IJCNLP,Ordonez:2016,zhao2017open}. As a starting point, we compare three popular datasets in  L\&V: RefCOCO, a collection of referring expressions, Flickr30k, a collection of captions, and VisualGenome, which features extensive region-level annotations. We observe that the object name annotations in these corpora suggests that there is a certain amount of variation, but the low number of annotations per item does not allow for any reliable assessment or analysis.

@@

Therefore, we contribute a new dataset, ManyNames, that contains 36 crowd-sourced names for 25K instances from \vg. Thus, the number of annotations per object available in ManyNames is considerably larger than in recent data collections in L\&V and can be used to compute agreement and related measures reliably.
Moreover, our images show objects in complex visual contexts,
unlike the ``clean'' ImageNet data~\cite{imagenet_cvpr09} which is popular in Computer Vision \cite{ILSVRC15}, and unlike stylized line drawings used in picture naming experiments in Cognitive Science (see Figure \ref{fig:cake}).
%

As illustrated for an object of the class ``cake'' in Figure \ref{fig:cake}, our data reveals clear naming preferences (53\% of the annotators prefer the basic-level \textit{cake}) and also rich variation (the remaining annotators prefer other options like \textit{food, dessert, bread}) which is not restricted to taxonomical relations studied in previous work on naming \cite{Ordonez:2016,graf2016animal}.

>>>>

Generally, research in Language \& Vision (L\&V) is interested in modeling how speakers \textit{naturally} talk about visual objects and scenes, in contrast to the fixed image labeling schemes used in Computer Vision.
Data collections in L\&V are typically set up as free annotation tasks,  where annotators (or speakers) are free to produce whatever word or utterance they consider most suitable for the given task (e.g.\ image description, reference to objects, visual dialogue) -- which necessarily results in linguistic variation.
For this reason, large-scale data collections in L\&V usually provide a certain amount of parallel annotations for the same entity from different annotators \cite{fangetal:2015,devlin:imcaqui,Kazemzadeh2014,mao15,vries2017guesswhat}.

As compared to work on perception and language grounding in Linguistics or Cognitive Science, however, recent data collections in L\&V capture a rather limited amount of inter-speaker variation.
For instance, so-called picture naming norms used in Psycholinguistics typically record naming responses for hundreds of speakers for the same object  \cite{snodgrass,rossion2004revisiting}, whereas captioning or referring expression data sets typically provide less than 10 annotations per entity \cite{devlin:imcaqui,Kazemzadeh2014,mao15}.
Consequently, a reliable assessment of inter-annotator agreement, speaker preferences and a deeper linguistic analysis of the observed variation is mostly out of scope with available data collections in  L\&V.
At the same time, these datasets provide more realistic images of real-world objects and scenes, and a wider coverage of object categories, compared to the idealized drawings used in picture naming norms, as shown in Figure \ref{fig:cake}.

In this paper, we take a first step towards building a dataset with object naming data for real-world images. We believe that a more systematic understanding of the factors underlying variation in object naming could inform theoretical work on language grounding and pragmatics \cite{rohde2012communicating,graf2016animal}, as well as the design of models and architectures in L\&V that deal with a large and natural vocabulary \cite{lazaridou-dinu-baroni:2015:ACL-IJCNLP,Ordonez:2016,zhao2017open}. As a starting point, we compare three popular datasets in L\&V: \refcoco, a collection of referring expressions, \flickr, a collection of captions, and \vgenome, which features extensive region-level annotations. We observe that the object name annotations in these corpora suggest that there is a certain amount of variation, but the low number of annotations per item does not allow for any reliable assessment or analysis.

@@

To address this shortcoming, we contribute a new dataset, ManyNames, that contains 36 crowd-sourced names for 25K instances from \vgenome.%
\footnote{The dataset will be available upon publication.}
The number of annotations per object available in ManyNames is considerably larger than in recent data collections in L\&V.
Moreover, our images show objects in complex visual contexts,
unlike the ``clean'' ImageNet data~\cite{imagenet_cvpr09} that is popular in Computer Vision \cite{ILSVRC15}, and unlike stylized line drawings used in picture naming experiments in Cognitive Science (Figure \ref{fig:cake}).

The trends we identify in the dataset are illustrated in Figure \ref{fig:cake} (left): Our data reveals clear naming preferences (in the example, 53\% of the annotators prefer the basic-level \textit{cake}) and also rich variation (the remaining annotators prefer other options like \textit{food, dessert, bread}) that is not restricted to taxonomical relations studied in previous work on naming \cite{Ordonez:2016,graf2016animal}.
